Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-05-30 prevalence_testing/postshocktest2022draft.tex
changes to manuscript

In this article our goal will be to leverage the post-shock information in the donor pool of series $y_{i,t}$, $i = 2,\ldots,n+1$ to test whether the anticipated shock is expected to be transient or persistent over the time horizon $H$ for the time series under study indexed by $i=1$. The methodology developed within will focus on the comparison of two forecasts for $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ where one forecast incorporates the shock effect and the other does not. We define these forecasts for each $i = 1,\ldots,n+1$, $t = 1,\ldots,T_i$ and $h = 1,\ldots,H$ as
$$
  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t},
$$
where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed shock and is based on the information set $\mathcal{F}_{t-h}$ (\textcolor{red}{need to define}), and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
%We are interested in point forecasts $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ with the aim of determining whether the shock has an effect on $y_{i,t}^h$.
%\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$. In our post-shock setting, we want to compare the forecasts 
%$$
%  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t}
%$$
%where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.

@@

Next, we define the $h$-step forecast for $\mc{M}$ which plays an essential role in the framework of \citet{quaedvlieg2021multi}. Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^{1,h}$. Let the ordinary least squares (OLS) estimate for
\begin{align*}
	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}', \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
\end{align*}
 be 
 \begin{align*}
 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}', \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
 \end{align*}
Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^{1,h}$ is defined as
 \begin{align*}
 	\hat{y}_{i,t}^{1,h} &= \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{1,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{1,h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\tilde{\bs{\theta}}}_{i,j+1},
 \end{align*}
 where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$. This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature (\textcolor{red}{either provide a citation or remove this sentence}). The $h$-step forecast corresponding to the model that does include any post-shock changes $\hat{y}_{i,t}^{2,h}$ is defined similarly,
\begin{equation*}
 	\hat{y}_{i,t}^{2,h} = \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{2,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right).
\end{equation*}

@@

In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting. The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
$$
  \dbf_{i,t} = \Llet_{i,t,1} - \Llet_{i,t,2},
$$
where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function. Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}. 
%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$. We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock. Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool. 
%%%\vspace*{0.5cm}
We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}. The aSPA investigates forecast comparisons based on their weighted average loss difference
$$
  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
$$
with weights $\textbf{w}_i$ that sum to one. Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1. With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.

@@

%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lK_i$. Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array 
$$
  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
$$
The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.

\begin{equation} \label{whb}
	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
\end{equation}
where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
\begin{equation} \label{boott}
  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
  \Big\vert \overset{P}{\longrightarrow} 0,
\end{equation}
as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
\begin{equation} \label{bootp}
  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
\end{equation}
The results \eqref{boott} implies that 
$$
  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
$$
where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$. Therefore bootstrap inference in the donor pool is a good approximation. %We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.

@@

The first approach is a weighted average of the p-values computed in the donor pool which are calculated as in Section \ref{sec:multhor}. The weights reflect the similarity between $\x_{i,T^*_i+1}$ and $\x_{1,T^*_1+1}$, and are similar to the weights computed in \cite{lin2021minimizing}. We now discuss the details. Let
\begin{align*}
	\bs{X}= \begin{pmatrix}
		\bs{x}_{1, T_1^*+1} & \cdots & \bs{x}_{1, T_1^*-q_2+1}\\
		\vdots &  \ddots & \vdots  \\
		\bs{x}_{n+1, T_{n+1}^*+1} & \cdots & \bs{x}_{1, T_1^*-q_2+1}
	\end{pmatrix}.
\end{align*}
The reason for including $\bs{x}_{i, T_i^*-q_2+1}$ is that the dynamic model \eqref{model-gen} considers lagged covariate values in its shock construction. Let $\mbf{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1. We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}. Note that the modeling part for the response $y_{i,t}$ does not necessarily involve scaled covariates. From this construction we obtain the weighted average p-value 
\begin{equation} \label{wpval}
 \hat{p}_1 = \sum_{i=2}^{n+1} w_i^* \hat{p}_i^B,	
\end{equation}
where $\hat{p}_i^B$ is given as \eqref{bootp} and $w_i^*$ is the weight corresponding to the similarity between the first and $(i+1)$th row of $\mbf{X}^*$.

We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool. \\

\textcolor{red}{Jilei, I want you to just describe what the voting method is in plain writing as I have done above with the weighted average p-value. The propositions can then follow.} \\

\textcolor{red}{Jilei, the algorithm needs to make explicit that a moving block bootstrap is performed.} \\

\textcolor{red}{the algorithms are described in Algorithm \ref{voting}. There are a couple of details that are worth noting. First, for $t = T_i+1$ and $i \geq 2$, we used to the methodology of \cite{lin2021minimizing} to compute point forecast for $\hat{y}_{i,t}^{2,h}$. Note that for $t = T_i+1$, using ordinary least square conditional forecast yields $\hat{y}_{i,t}^{2,h}=  \hat{y}_{i,t}^{1,h}$ as those two forecast just differ by shock information, which is not available at this time point. We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions. Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$. It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis. }

\vspace{.5cm}
\begin{algorithm}
\SetAlgoLined \label{voting}

\SetKwInOut{Input}{Input}
\Input{$B, \ell $ --  bootstrap sample size, the  block size \textcolor{red}{Where is bootstrapping used in this algorithm?},   \\ 
$\gamma$ -- bandwidth parameter in heteroskedasticity and autocorrelation  consistent covariance \\ 
	\quad \quad matrix  estimation.\\ 
$\alpha$ -- significance level\\$\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\
$\{K_i \colon i = 2, \ldots, n+1\}$  -- training sample size for $h$-step forecast for different time series \\
$q_1, q_2$ -- user-specified parameters in $\mc{M}$ \\
$H$ -- maximum horizon 
}

@@

 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
 		}
 		Compute the squared error loss $l_{t,h}^1$ based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{1, h}$\\
 		 Compute the squared error loss $l_{t,h}^2$ based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{2, h}$
 		}
 	}
 	Construct the loss differential matrix with element $l_{t,h}^2-l_{t,h}^1$ at $t$th row and $h$th column \\
 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{t,h}^2-l_{t,h}^1\}_{t,h}$ \textcolor{red}{please confirm that this is the same notation as before.} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i$\\
  }

@@

@@

From the definition of $D_{i,t} = I(t > T_i^*+1)$, it is evident that the number of post-shock time points, i.e., time $t$ for which $t > T_i^*+1$, affects the inference results. As our methodology only requires $T_i-T_i^*$ is not small compared to $T_i$, we attempted three post-shock time length for our inference, say $L = 7, 15, 30$. Recall that in  Section \ref{section2}, we refer to the forecast  that incorporates shock information as adjusted forecast and the one that does not as unadjusted forecast. As specified in Section \ref{section2}, post-shock prevalence testing requires specification of  the maximum number $H$ of forecast horizons and training sample size $K$, where $h$-step forecasts of adjusted forecast and unadjusted forecast are compared for $h = 1, \ldots, H$. We set $H = 10$, $K = 30$, and $T_i =  H + K + L+15$ for $i = 2, \ldots, 4$. That being said, for $t = K + H + 1, \ldots, T_i$ and $h = 1, \ldots, H$, different $h$-step adjusted and unadjusted forecasts for $y_{i,t}$ under $\mc{M}_0$ or  $\mc{M}$ are compared.

>>>>

In this article our goal will be to leverage the post-shock information in the donor pool of series $y_{i,t}$, $i = 2,\ldots,n+1$ to test whether the anticipated shock is expected to be transient or persistent over the time horizon $H$ for the time series under study indexed by $i=1$. The methodology developed within will focus on the comparison of two forecasts for $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ where one forecast incorporates the shock effect and the other does not. We define these forecasts for each $i = 1,\ldots,n+1$, $t = 1,\ldots,T_i$ and $h = 1,\ldots,H$ as
$$
  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t},
$$
where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
%We are interested in point forecasts $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ with the aim of determining whether the shock has an effect on $y_{i,t}^h$.
%\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$. In our post-shock setting, we want to compare the forecasts 
%$$
%  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t}
%$$
%where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.

@@

Next, we define the $h$-step forecast for $\mc{M}$ which plays an essential role in the framework of \citet{quaedvlieg2021multi}. Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^{1,h}$. Let the ordinary least squares (OLS) estimate for
\begin{align*}
	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}', \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
\end{align*}
 be 
 \begin{align*}
 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}', \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
 \end{align*}
Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^{1,h}$ is defined as
 \begin{align*}
 	\hat{y}_{i,t}^{1,h} &= \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{1,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{1,h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\tilde{\bs{\theta}}}_{i,j+1},
 \end{align*}
 where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$. The $h$-step forecast corresponding to the model that does include any post-shock changes $\hat{y}_{i,t}^{2,h}$ is defined similarly,
\begin{equation*}
 	\hat{y}_{i,t}^{2,h} = \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{2,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right).
\end{equation*}

@@

In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting. The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
$$
  \dbf_{i,t} =  \textcolor{red}{\Llet_{i,t,2} - \Llet_{i,t,1}},
$$
where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function. Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}. 
%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$. We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock. Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool. 
%%%\vspace*{0.5cm}
We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}. The aSPA investigates forecast comparisons based on their weighted average loss difference
$$
  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
$$
with weights $\textbf{w}_i$ that sum to one. Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1. With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.

\textcolor{red}{Define $\mbf{D}_i = (\mbf{d}_{i, T^*_i+H+1}', \ldots, \mbf{d}_{i, T_i}')$, which is the loss differential matrix of $i$th time series. Note that $\mbf{D}_i$ is of dimension $T_i-T^*_i - H$.   $\mbf{D}_i$ compares $h$-step forecasts of $y_{i, t}$ for $t = T^* + H + 1$ to $t = T$ and $h= 1, \ldots, H$. In this design, adjusted and unadjusted forecasts are different with probability one such that elements of $\mbf{D}_i$ are different from zero with probability one. This prevents excessive zeroes to affect our inference results if $t = H+K +1,  \ldots, T$, where $K$ is the training sample size for parameter estimation of $h$-step forecasts.}

@@

%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = l\textcolor{red}{U_i}$. Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array 
$$
  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
$$
The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.

\begin{equation} \label{whb}
	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{\textcolor{red}{U_i}}\sum_{k=1}^{\textcolor{red}{U_i}}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
\end{equation}
where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
\begin{equation} \label{boott}
  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
  \Big\vert \overset{P}{\longrightarrow} 0,
\end{equation}
as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
\begin{equation} \label{bootp}
  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
\end{equation}
The results \eqref{boott} implies that 
$$
  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
$$
where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$. Therefore bootstrap inference in the donor pool is a good approximation. %We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.

@@

The first approach is a weighted average of the p-values computed in the donor pool which are calculated as in Section \ref{sec:multhor}. The weights reflect the similarity between $\x_{i,T^*_i+1}$ and $\x_{1,T^*_1+1}$, and are similar to the weights computed in \cite{lin2021minimizing}. We now discuss the details. Let
\begin{align*}
	\bs{X}= \begin{pmatrix}
		\bs{x}_{1, T_1^*+1}  \\
		\vdots   \\
		\bs{x}_{n+1, T_{n+1}^*+1} 
	\end{pmatrix}.
\end{align*}
\textcolor{red}{In this paper, we consider this simple form of $\bs{X}$ for illustrative purpose. However,  more general $\bs{X}$'s are allowable. For example, $\bs{X}$ can also include $\bs{x}_{i, T_i^*-j+1}$ for $j = 2, \ldots, q_2$, which considers the lagged covariates in the dynamic model \eqref{model-gen}.} Let $\bs{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1. We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}. Note that the modeling part for the response $y_{i,t}$ does not necessarily involve scaled covariates. From this construction we obtain the weighted average p-value 
\begin{equation} \label{wpval}
 \hat{p}_1 = \sum_{i=2}^{n+1} w_i^* \hat{p}_i^B,	
\end{equation}
where $\hat{p}_i^B$ is given as \eqref{bootp} and $w_i^*$ is the weight corresponding to the similarity between the first and $(i+1)$th row of $\mbf{X}^*$.

We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool. \textcolor{red}{Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote}
\begin{align*}
	V = I\Big\{\frac{1}{n} \sum_{i=2}^{n+1} I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\},
\end{align*}
\textcolor{red}{where $I(\cdot)$ is an indicator function. The idea of voting is very intuitive in the sense that donors vote for the shock persistence or transience  using a hypothesis testing approach and the one receiving more votes is returned.  Second, the weighted voting generalizes this idea by making using of  the similarity weights $\mbf{W}^*$. It is defined as }
\begin{align*}
	V^* = I\Big\{ \sum_{i=2}^{n+1} w_i^* I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\}.
\end{align*}

\textcolor{red}{Algorithm \ref{Bu} describes the mechanics of computing $\mbf{W}^*, \hat{p}_1, V, V^*$ in more detail. There are a couple of details that are worth noting. First, for $t = T_i+1$ and $i \geq 2$, we used to the methodology of \cite{lin2021minimizing} to compute point forecast for $\hat{y}_{i,t}^{2,h}$. Note that for $t = T_i+1$, using ordinary least square conditional forecast yields $\hat{y}_{i,t}^{2,h}=  \hat{y}_{i,t}^{1,h}$ as those two forecast just differ by shock information, which is not available at this time point. We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions. Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$. It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis. }

\vspace{.5cm}
\begin{algorithm}
\SetAlgoLined

\SetKwInOut{Input}{Input}
\Input{$B, \ell $ --  bootstrap sample size, the  block size  \\ 
$\gamma$ -- bandwidth parameter in heteroskedasticity and autocorrelation  consistent covariance \\ 
	\quad \quad matrix  estimation.\\ 
$\alpha$ -- significance level\\$\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\
$\{K_i \colon i = 2, \ldots, n+1\}$  -- training sample size for $h$-step forecast for different time series \\
$q_1, q_2$ -- user-specified parameters in $\mc{M}$ \\
$H$ -- maximum horizon 
}

@@

 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
 		}
 		Compute the squared error loss \textcolor{red}{$l_{i,t,h, 1}$} based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{1, h}$\\
 		 Compute the squared error loss \textcolor{red}{$l_{i,t,h, 2}$} based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{2, h}$
 		}
 	}
 	Construct the loss differential matrix   with element \textcolor{red}{$l_{i,t,h, 2}-l_{i,t,h, 1}$} at $t$th row and $h$th column \\
 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix \textcolor{red}{$\{l_{i,t,h,2}-l_{i,t,h,1}\}_{t,h}$} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i^B$, \textcolor{red}{where the test uses moving block bootstrap   with $B$ and $\gamma$.}\\
  }

@@

\label{sec::ne}

@@

\textcolor{red}{Regarding the hyper-parameters, in this data example, we set $T_i- T_i^* = 30$ and $K = 30$. Note that $K = 30$ is a sensible  training sample size, see discussions for example in  \cite{lin2021minimizing}. Also, $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.  We set $T_i- T_i^* = 30$  in order to make the post-shock time length moderately large and also for illustration purpose. For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.}

\textcolor{red}{We summarize our numerical results in Table \ref{coptable}. In the Table \ref{coptable}, $p_1$ stands for the forecast comparison test of \cite{quaedvlieg2021multi} applied for adjusted and unadjusted forecasts on the time series of interest. Note that in practice, it cannot be computed because  $y_{1, t}$ for $t > T_1^*$ is not observed. It is provided   for retrospective  analysis. Second, $\hat{p}_1$ is the  estimate for $p_1$ using $\mbf{W}^*$.  We recorded the voting and weighted voting results in the form of indicators with one being voting for persistence and zero for transience. See the methodological details for $\hat{p}_1$, voting, and weighted voting in Section \ref{sec:multhor}. In companion with the voting, the correctness of the voting is evaluated and provided  in the brackets. For example, ``0 (Yes)'' implies  that the procedure votes for transience and this decision is correct whereas ``1 (No)'' votes for persistence and it is incorrect.  }

\begin{table}[H]
	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.183, 0, 0.817)$ from scaled covariates} \label{coptable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $H$  & Model &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     \multirow{2}{*}{2} & $\mc{M}_0$  &   1 & 0.183  & 0.817 & 0 (Yes) & 1 (No)  \\      
      & $\mc{M}$  & 1 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
     \multirow{2}{*}{4} & $\mc{M}_0$ &   0 & 0.519  & $0.519$ & 0 (No) &1 (No)    \\
      &  $\mc{M}$ & 1& 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
     \multirow{2}{*}{6} &  $\mc{M}_0$ &   0   & $0.817$ & 0.817 & 0 (No) &1 (No)   \\
      &  $\mc{M}$ & 1 & 1  & 0 &0 (Yes) & 0 (Yes) \\[.2cm]
     \multirow{2}{*}{8} & $\mc{M}_0$ & 0  & 0.817 & 0.817 & 0 (No) & 0 (No)\\
     & $\mc{M}$ & 1 & 1 & 0 & 0 (Yes) & 0 (Yes)
  \end{tabular}
\end{center}	
\end{table}
